\documentclass[11pt]{article} 
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage[siunitx]{circuitikz}
\usepackage{tikz}
\usepackage[colorinlistoftodos, color=orange!50]{todonotes}
\usepackage{hyperref}
\usepackage[numbers, square]{natbib}
\usepackage{fancybox}
\usepackage{epsfig}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage[version=4]{mhchem}
\usepackage{multicol}

\usepackage{mathtools}
\usepackage{comment}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{listings}
\usepackage{color}
\usepackage[numbers]{natbib}
\usepackage{subfiles}
\usepackage{tkz-berge}


\newtheorem{prop}{Proposition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{cor}{Corollary}[prop]

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{definition}
\newtheorem{required}{Problem}

\theoremstyle{definition}
\newtheorem{ex}{Example}


\setlength{\marginparwidth}{3.4cm}
%#########################################################

%To use symbols for footnotes
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
%To change footnotes back to numbers uncomment the following line
%\renewcommand*{\thefootnote}{\arabic{footnote}}

% Enable this command to adjust line spacing for inline math equations.
% \everymath{\displaystyle}

% _______ _____ _______ _      ______ 
%|__   __|_   _|__   __| |    |  ____|
%   | |    | |    | |  | |    | |__   
%   | |    | |    | |  | |    |  __|  
%   | |   _| |_   | |  | |____| |____ 
%   |_|  |_____|  |_|  |______|______|
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{
\normalfont \normalsize 
\textsc{CSCI 3104 Fall 2021 \\ 
Instructor: Profs. Grochow and Waggoner} \\
[10pt] 
\rule{\linewidth}{0.5pt} \\[6pt] 
\huge Quiz- Standard 5 \\
\rule{\linewidth}{2pt}  \\[10pt]
}
%\author{Your Name}
\date{}

\begin{document}

\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%FILL IN YOUR NAME%%%%%%%
%%%%%%%%%%AND STUDENT ID%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
Due Date \dotfill October / $1^{st}$ / 2021 \\
Name \dotfill \textbf{Michael Ghattas} \\
Student ID \dotfill \textbf{109200649} \\


\tableofcontents

\section{Instructions}
 \begin{itemize}
	\item The solutions \textbf{should be typed}, using proper mathematical notation. We cannot accept hand-written solutions. \href{http://ece.uprm.edu/~caceros/latex/introduction.pdf}{Here's a short intro to \LaTeX.}
	\item You should submit your work through the \textbf{class Canvas page} only. Please submit one PDF file, compiled using this \LaTeX \ template.
	\item You may not need a full page for your solutions; pagebreaks are there to help Gradescope automatically find where each problem is. Even if you do not attempt every problem, please submit this document with no fewer pages than the blank template (or Gradescope has issues with it).

	\item You \textbf{may not collaborate with other students}. \textbf{Copying from any source is an Honor Code violation. Furthermore, all submissions must be in your own words and reflect your understanding of the material.} If there is any confusion about this policy, it is your responsibility to clarify before the due date. 

	\item Posting to \textbf{any} service including, but not limited to Chegg, Discord, Reddit, StackExchange, etc., for help on an assignment is a violation of the Honor Code.

	\item You \textbf{must} virtually sign the Honor Code (see Section \ref{HonorCode}). Failure to do so will result in your assignment not being graded.
\end{itemize}


\section{Honor Code (Make Sure to Virtually Sign)} \label{HonorCode}

\begin{required}
\noindent 
\begin{itemize}
\item My submission is in my own words and reflects my understanding of the material.
\item I have not collaborated with any other person.
\item I have not posted to external services including, but not limited to Chegg, Discord, Reddit, StackExchange, etc.
\item I have neither copied nor provided others solutions they can copy.
\end{itemize}

%\noindent In the specified region below, clearly indicate that you have upheld the Honor Code. Then type your name. 
\end{required}

\begin{proof}[I agree to the above, Michael Ghattas.]
%% Typing "I agree to the above," followed by your name is sufficient.
\end{proof}



\newpage
\section{Standard 5- Exchange Arguments}

\subsection{Problem \ref{DFS1}}
\begin{required} \label{DFS1}
Suppose that there are $n$ homework assignments, where the $i$th homework assignment has difficulty $d_{i}$. All of the assignments are released on the first day of class, and you may turn in one assignment per week. If you turn in assignment $i$ on week $k$, then you receive $d_{i}(n-k)$ points. Do the following.

\begin{enumerate}[label=(\alph*)]
\item Consider a solution in which you turn in assignment $j$ before assignment $i$, even though $d_{j} > d_{i}$. Show that you can increase the number of points earned by turning in assignment $j$ before assignment $i$.

\begin{proof}[Answer:] \
\begin{itemize}
\item \textbf{Let n = Number of assignments $\to$} $n\in\mathbb{N}$
\item \textbf{Let k = Number of weeks = $\{k_i,...,k_j\}$, where $(k_j > k_i) \to$} $k\in\mathbb{N}$
\item \textbf{We assume $\to$ $n = |k|$}
\item \textbf{Thus $\to$ $(n - k_i) > (n - k_j)$} \\
\item \textbf{Let d = Assignment difficulty level = $\{d_i,...,d_j\}$, where $(d_j > d_i) \to$} $d\in\mathbb{N}$
\item \textbf{Accordingly $\to$ $d_i(n - k_i) > d_i(n - k_j)$, and $d_j(n - k_i) > d_j(n - k_j)$}
\item \textbf{Since $(d_j > d_i)$ $\to$ $d_j(n - k_i) > d_i(n - k_i)$} \\
\item \textbf{Thus $\to$ $d_j(n - k) > d_i(n - k)$, as desired.}
\end{itemize}
%Your answer here.
\end{proof}


\vskip 50pt
\item Using part (a), describe a greedy algorithm to order the assignments in order to maximize the number of points earned. Pseudo-code is not required, but you should provide enough detail that a CSCI 2270 student could reasonably be expected to implement the solution from your description.

\begin{proof}[Answer:] \
\item \textbf{Algorithm pseudocode:}
\item \textbf{function} GradeMax(assignment[Number, Difficulty], Week(int)):									
	\item	\hspace*{10mm} Number = length(assignment(Number))
	\item	\hspace*{10mm} assignment due = 0
	\item	\hspace*{10mm} AssignmentList[] = 0

	\item	\hspace*{10mm} for i in Number:
	\item	\hspace*{20mm} while assignment[Difficulty] < assignment[Difficulty + 1]:
	\item	\hspace*{40mm} assignment due = assignment[Difficulty + 1)]
	\item	\hspace*{30mm} if (assignment due == assignment(Difficulty)):
	\item	\hspace*{40mm} assignment due == assignment(Number)
	\item	\hspace*{40mm} AssignmentList[i] == assignment due
	\item	\hspace*{10mm} return AssignmentList[];

%Your answer here
\end{proof}

\end{enumerate}
\end{required}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document} % NOTHING AFTER THIS LINE IS PART OF THE DOCUMENT



